---
title: " Class1  Execrcise"
output: html_notebook
---
## The R code


```{r}

firstvar
```
##Create and store a character vector (of your choice), 
a numeric vector (interger/double) and a factor, all of the same length

```{r}
Salesregions <- c("NA","Europe","Asia Pacific")
Sales <-c(200,300,400.0)
length (Salesregions)
length (Sales)

```
2. Use `seq()` to generate an atomic vector containing all the odd numbers less than 100
```{r}
seq(from = 99, to = 1, by = -2.0)
```

3. Store all the vectors created in step 1 in a named list
```{r}
testlist <- list(Salesregions,Sales)
testlist
```

4. Create a dataframe using all the vectors stored in step 1
```{r}
regionaldata <- data.frame(Region = Salesregions, SalesAmount = Sales)
regionaldata

```

regionaldata <- data.frame(Region = Salesregions, Sales Amount = sales)

5. Predict the output of the following without running the code in 
`+ c("FALSE", FALSE)`- "Character",
`+ c(1.0, FALSE)- "Double"`, `
 + c(2, TRUE)- "Double", 
`+c("two", 2)- "character"`

6. What get returned when you check the `typeof()` the dataframe created in step 4. Why?

```{r}
typeof(regionaldata)

```
```{r}
install.packages("tidyverse")
```
```{r}
vignette(package = "ggplot2")

```

